cardinalR: Generating interesting high-dimensional data structures

### 2025-04-25 paper-cardinalR.Rmd
Updated the application

```{r load-libraries}
library(cardinalR)
library(tidyverse)
library(kableExtra)
library(geozoo)
library(patchwork)
library(GGally)
library(ggdendro)
library(mulgar)
```

@@

We illustrate the use of the package by generating five clusters of different shapes, positioned with equal inter-cluster distances in $4\text{-}D$. Using this synthetic dataset, we will evaluate the performance of six popular dimensionality reduction techniques: Principal Component Analysis (PCA) [@jolliffe2011], t-distributed stochastic neighbor embedding (tSNE) [@laurens2008], uniform manifold approximation and projection (UMAP) [@leland2018], potential of heat-diffusion for affinity-based trajectory embedding (PHATE) algorithm [@moon2019], large-scale dimensionality reduction Using triplets (TriMAP) [@amid2019], and pairwise controlled manifold approximation (PaCMAP) [@yingfan2021].

@@

```{r}
langevitour::langevitour(five_clusts[, -5])
```

@@

```{r layouts}
tsne_data <- read_rds("data/five_clusts/five_clusts_tsne_perplexity_30.rds")

>>>>

```{r load-libraries}
library(cardinalR)
library(tidyverse)
library(kableExtra)
library(geozoo)
library(patchwork)
library(colorspace)
```

@@

We illustrate the use of the package by generating five clusters of different shapes, positioned with equal inter-cluster distances in $4\text{-}D$. Using this synthetic dataset, we will evaluate the performance of six popular dimension reduction techniques: Principal Component Analysis (PCA) [@jolliffe2011], t-distributed stochastic neighbor embedding (tSNE) [@laurens2008], uniform manifold approximation and projection (UMAP) [@leland2018], potential of heat-diffusion for affinity-based trajectory embedding (PHATE) algorithm [@moon2019], large-scale dimensionality reduction Using triplets (TriMAP) [@amid2019], and pairwise controlled manifold approximation (PaCMAP) [@yingfan2021].

@@

```{r, eval=FALSE}
langevitour::langevitour(five_clusts[, -5])
```

@@

```{r layouts}
clusters <- as.vector(five_clusts[, 5])

tsne_data <- read_rds("data/five_clusts/five_clusts_tsne_perplexity_30.rds")
